SoK: Transparent Dishonesty: front-running attacks on Blockchain.

### 2018-12-08 frontrunning/Latex/sections/paper.tex
[frontrunning] bcash abc ref

An alternative is to sequence transactions psuedorandomly. This can be seen in proposals like Canonical Transaction Ordering Rule (CTOR) in Bitcoin cash which adds transactions in lexicographical order according to their hash~\cite{bitcoinABC2018CTOR}. Note that Bitcoin cash does not have a front-running problem for most standard transactions. While this could be used by Ethereum to make front-running statistically difficult, the protection is marginal at best and might even exacerbate attacks. A front-runner can construct multiple equivalent transactions, with slightly different values, until she finds a candidate that positions her transaction a desirable location in the resulting sequence. She broadcasts only this transaction and now miners that include her transaction will position it in front of transactions they heard about much earlier.

@@

A DApp includes the following components: (1) the code of the DApp, (2) the current state of the DApp, (3) the name of the function being invoked, (4) the parameters supplied to the function, (5) the address of the contract the function is being invoked on, and (6) the identity of the sender. Confidentiality applied to a DApp could mean different levels of protection for each of these. For front-running, function calls (3,4) are the most important, however function calls could be inferred from state changes (2). Hawk~\cite{kosba2016hawk} and Eiden [c] are examples of (2,3,4)-confidentiality (with limitations we are glossing over).

The applicability of privacy-preserving blockchains needs to be evaluated on a case-by-case base. For example, one method used by traditional financial exchanges in dealing with front-running from high frequency traders is a dark market: essentially a (2,3,4)-confidential order book maintained by a trusted party. A DApp could disintermediate this trusted party. Users whose balances are effected by changes in the contract's state would need to be able to learn this information. Further, if the contract addresses are known (no 5-confidentiality), front-runners can know about the traffic pattern of calls to contracts which could be sufficient grounds for attack; for example, if each asset on an exchange has its own market contract, this leaks trade volume information. As a contrasting example, consider again decentralized domain registration: hiding state changes (2-confidentiality) defeats the entire purpose of the DApp, and protecting function calls is ineffective with a public state change since the state itself reveals the domain being registered.

@@

While confidentiality appears insufficient for solving domain name front-running alone, a hybrid approach of sequencing and confidentiality can be effective, and is in fact an example of an older cryptographic trick known as commit/reveal. The essence of the approach is to protect the function call (\eg (3,4)- or (4)-confidentiality) until the function is enqueued in sequence of functions to be executed. Once the sequence is established, the confidentiality is lifted and the function can only be executed in the place is was given (or, generally speaking, not at all).

Recall that a commitment scheme enables one to commit to a digital value (\eg a statement, transaction, data, \etc) while keeping it a secret (\textit{hiding}), and then open it (and only it: \textit{binding}) at a later time of the committer's choosing~\cite{brassard1988minimum}. A common approach (conjectured to be hiding) is to submit the cryptographic hash of the value with a random nonce (for low entropy data) to a smart contract, and later reveal the original value and nonce which can be verified by the contract to correctly hash to the commitment (see Figure~\ref{fig:commitReveal} in Appendix~\ref{app:cr}).

An early application of this scheme to blockchain is Namecoin, a Bitcoin-forked DApp for name services~\cite{kalodner2015empirical}. In Namecoin, a user sends a commit transaction which registers a new hidden domain name, similar to a sealed bid. Once this first transaction is confirmed, a time delay begins. After the delay, a second transaction reveals the details of the requested domain. This prevent front-running if the reveal transaction is confirmed faster than an adversarial node or miner can redo the entire process.

Commit/reveal is a two round protocol, and aborting after the first round (early aborts) could be an issue for this (along with most multi-round cryptographic protocols). For example, in a financial exchange where the number of other orders might be in a predictable interval, an adversary can spray the sequence (\ie a price-time priority queue) with multiple committed transactions and no intention of executing them all. She then only reveal the ones that result in an advantageous trade.\footnote{This is analogous to behaviour in traditional financial markets where high frequency traders will make and cancel orders at many price points. If they can cancel faster than someone can execute it---someone who has only seen the order and not the cancelation---then the victim reveals their price information.} There are other ways of aborting; if payments are required but not collateralized, the aborting party can ensure that payment is not available for transfer. One mitigation to early aborts that blockchain is uniquely positioned to make is having users post a fidelity bond of a certain amount of cryptocurrency that can be automatically dispensed if they fail to fully execute committed transactions (this is used in multi-round blockchain voting~\cite{mccorry2017smart}). Finally we note that any multiple round protocol will have usability challenges: users must be aware that participating in the first round is not sufficient for completing their intention.

% Jeremy: doesn't seem related to front-running
%Commit/reveal is also seen in on-chain voting~\cite{adChainPLCRVoting}. Using sealed votes, voters can assure their votes are hidden until a later date, however, their participation and weight of the vote are publicly known.

% Jeremy: moved up to confidentiality as this is not specific to commit/reveal but applicable to any mitigation
%The participatory factor is another issue for the commitment scheme. For anyone watching the DApp address, there will be a direct transaction from the user to the DApp address, revealing the fact that a specific address has participated in the auction or the DApp using a commit and reveal scheme, but the details are hidden through the scheme. Both these issues, albeit hiding the details of the order and preventing direct front-running, leak information to other participants which could lead to more sophisticated front-running attacks depending on the application design. On the other note, these method has some drawbacks, the user experience is not smooth and one might forget to reveal the committed transaction. In the ENS commit-reveal process, if one forgets to reveal in the reveal phase, the committed funds are burnt and inaccessible thereafter. Also, this scheme means two transactions are required for a functionality which makes it more expensive.

\begin{figure}[t]
\centering
\includegraphics[width=0.5\linewidth]{figures/LibSubmarine.png}
\caption{Submarine Send~\cite{libsubmarine}. User generates an \textit{Unlock} transaction from which the commitment address is retrieved. By funding the \textit{commitment address}, user is committed to the unlock transaction. After the commitment transaction, in the reveal phase, user sends the \textit{reveal transaction} to the DApp and then after she can broadcast the Unlock transaction to unlock the funds in the commitment address. Finally after the "Auction'' is over, anyone can call \textit{Finalize} function to finalize the process.  \label{fig:LibSubmarine}}
\end{figure}
%https://www.lucidchart.com/invitations/accept/3a259b74-1162-4fb5-8023-eb0311018295

\paragraph{Enhanced Commit/Reveal.} Submarine Commitments~\cite{breidenbach2018enter,submarinesendHD} extend basic commit/reveal functionality with additional properties for Ethereum smart contracts: (1) they initially hide the contract address being invoked, providing (3,4,5)-confidentiality during the commit phase; and (2) they ensure that if a revealed transaction sent funds, the funds were fully collateralized at commit time and are available to the receiving smart contract.

% Jeremy: Merge this into the caption so there is one stand-alone description
%With submarine send, it is possible to hide sender, receiver, value, and data, so the commitment transaction is identical to a transaction to a newly generated address. Submarine sends could be a solution for sealed-bid auctions on the blockchain to hide the existence of the bids for other participants. The details of how Submarine commitments work could fill an entire paper, however in short, using the way Ethereum transactions are constructed and ECDSA ECRecover functionality, it is possible to generate one outgoing transaction from an address of which no private key exists. By constructing a transaction from that address to the DApp and funding that address we fulfill the commitment phase. By revealing the details and broadcasting the constructed transaction we reveal the commitment~\cite{libsubmarine}. See Figure~\ref{fig:LibSubmarine}. However, this could be designed in other ways to suit the need of the DApp. Drawbacks of this scheme are similar to commit/reveal, with the addition of two more transactions to finalize a transaction, which adds cost and complexity to the user experience.

@@

The final main category of mitigation is to assume front-running is unpreventable and to thus responsively redesign the functionality of the DApp to remove any benefit from front-running. For example, when designing a decentralized exchange, one can use a call market design instead of a time-sensitive order book~\cite{clark2014decentralizing} to side-step and disincentivize front-running by miners. In a call market design, the arrival time of orders does not matter as they are executed in batches. The call market solution pivots profitable gains that front-running miners stand to gain into fees that they collect~\cite{clark2014decentralizing}, removing the financial incentive to front-run. To the same end, Malinova~\cite{malinova2017market} proposes a design for a decentralized exchange which uses economic models in their trading market design to make front-running expensive and more costly than profitable. They split big investments into smaller ones using intermediaries --liquidity demander-- and liquidity providers to achieve this.

% one solution could be to remove multiple actors, meaning that on each "play" (order), the smart contract would be the market maker. it does not matter if there are multiple similar orders. similar to PoC of Velocity~\cite{eskandari2017feasibility}. Although there are other concerns about this specific design but not for front-running.
%TODO: inline talk about what these solutions are good for and if they fit Status ICO

>>>>

An alternative is to sequence transactions psuedorandomly. This can be seen in proposals like Canonical Transaction Ordering Rule (CTOR) by Bitcoin Cash ABC~\cite{bitcoincashabcFork} which adds transactions in lexicographical order according to their hash~\cite{bitcoinABC2018CTOR}. Note that Bitcoin does not have a front-running problem for most standard transactions. While this could be used by Ethereum to make front-running statistically difficult, the protection is marginal at best and might even exacerbate attacks. A front-runner can construct multiple equivalent transactions, with slightly different values, until she finds a candidate that positions her transaction a desirable location in the resulting sequence. She broadcasts only this transaction and now miners that include her transaction will position it in front of transactions they heard about much earlier.

@@

A DApp includes the following components: (1) the code of the DApp, (2) the current state of the DApp, (3) the name of a function being invoked, (4) the parameters supplied to the function, and (5) the identity of the sender. Confidentiality applied to a DApp could mean different levels of protection for each of these. For front-running, function calls (3,4) are the most important, however function calls could be inferred from state changes (2). Hawk~\cite{kosba2016hawk} and Eiden [c] are examples of (2,3,4)-confidentiality (with limitations we are glossing over).

The applicability of privacy-preserving blockchains needs to be evaluated on a case-by-case base. For example, one method used by traditional financial exchanges in dealing with front-running from high frequency traders is a dark market: essentially a (2,3,4)-confidential order book maintained by a trusted party. A DApp could disintermediate this trusted party. Users whose balances are effected by changes in the contract's state would need to be able to learn this information. As a contrasting example, consider again decentralized domain registration: keeping the state confidential defeats the entire purpose of the DApp. Only protecting function calls is ineffective as the state change itself reveals which domain is attempting to be registered.

@@

While confidentiality appears insufficient for solving domain name front-running alone, a hybrid approach of sequencing and confidentiality can be effective, and is in fact an example of an older cryptographic trick known as commit/reveal. The essence of the approach is to protect the function call, \ie (3,4)-confidentiality, until the function is enqueued in sequence of functions to be executed. Once the sequence is finalized, the confidentiality is lifted and the function can only be executed in the place is was given (or, generally speaking, not at all).

A commitment scheme is a cryptographic primitive that enables one to commit to a value (\eg a statement, document, data, \etc) while keeping it a secret, and then open it (and only it) at a later time of the committer's choosing~\cite{brassard1988minimum}. A common approach is to submit the hash value of the data to be committed, potentially with a random nonce (for predictable data), to a smart contract and later reveal the original data and nonce which can be verified to hash to the commitment. See Figure~\ref{fig:commitReveal} in Appendix~\ref{app:cr}.

An early use of this scheme is Namecoin, a Bitcoin-forked blockchain for name services~\cite{kalodner2015empirical}. In Namecoin, a user sends a commit transaction which commits to the name hash, similar to a sealed bid. Once the transaction is confirmed and the grace period is over, the user sends a reveal transaction revealing the bid and also the details of the requested domain~\cite{kalodner2015empirical}. Hence, the user is able to hide information from the adversarial parties in the system and prevent front-running attacks.

In the case of decentralized exchanges, users can use commit/reveal for bids, where commitments are placed in an ordered queue and executed in a later round after a reveal. This mitigation seems to require further research. One trader strategy is to flood orders at the commitment stage, but then only selectively and adaptively choose which to reveal. Collateralization is another challenge, where revealed bids may simply be intentions to execute but additional transactions are required to move the money or tokens; a transaction that can also be aborted early. One mitigation to early aborts is having users post a fidelity bond that can be automatically dispensed if they fail to fully execute committed transactions (as used in~\cite{mccorry2017smart}). Commit/reveal is also seen in on-chain voting~\cite{adChainPLCRVoting}. Using sealed votes, voters can assure their votes are hidden until a later date, however, their participation and weight of the vote are publicly known.

The participatory factor is another issue for the commitment scheme. For anyone watching the DApp address, there will be a direct transaction from the user to the DApp address, revealing the fact that a specific address has participated in the auction or the DApp using a commit and reveal scheme, but the details are hidden through the scheme. Both these issues, albeit hiding the details of the order and preventing direct front-running, leak information to other participants which could lead to more sophisticated front-running attacks depending on the application design. On the other note, these method has some drawbacks, the user experience is not smooth and one might forget to reveal the committed transaction. In the ENS commit-reveal process, if one forgets to reveal in the reveal phase, the committed funds are burnt and inaccessible thereafter. Also, this scheme means two transactions are required for a functionality which makes it more expensive.

\begin{figure}[t]
\centering
\includegraphics[width=0.5\linewidth]{figures/LibSubmarine.png}
\caption{ Submarine Send~\cite{libsubmarine}. User generates an \textit{Unlock} transaction from which the commitment address is retrieved. By funding the \textit{commitment address}, user is committed to the unlock transaction. After the commitment transaction, in the reveal phase, user sends the \textit{reveal transaction} to the DApp and then after she can broadcast the Unlock transaction to unlock the funds in the commitment address. Finally after the "Auction'' is over, anyone can call \textit{Finalize} function to finalize the process.  \label{fig:LibSubmarine}}
\end{figure}
%https://www.lucidchart.com/invitations/accept/3a259b74-1162-4fb5-8023-eb0311018295

Submarine Commitments~\cite{breidenbach2018enter,submarinesendHD} extend basic commit/reveal functionality with additional properties. In particular, they hide the DApp being invoked during the commit phase and also ensure that revealed transactions that send funds are fully collateralized. With submarine send, it is possible to hide sender, receiver, value, and data, so the commitment transaction is identical to a transaction to a newly generated address. Submarine sends could be a solution for sealed-bid auctions on the blockchain to hide the existence of the bids for other participants. The details of how Submarine commitments work could fill an entire paper, however in short, using the way Ethereum transactions are constructed and ECDSA ECRecover functionality, it is possible to generate one outgoing transaction from an address of which no private key exists. By constructing a transaction from that address to the DApp and funding that address we fulfill the commitment phase. By revealing the details and broadcasting the constructed transaction we reveal the commitment~\cite{libsubmarine}. See Figure~\ref{fig:LibSubmarine}. However, this could be designed in other ways to suit the need of the DApp. Drawbacks of this scheme are similar to commit/reveal, with the addition of two more transactions to finalize a transaction, which adds cost and complexity to the user experience.

@@

Front-running can be tackled at the blockchain layer, as seen in the previous section, or mitigations can be built at the DApp level as seen here.

The applications can be designed not to rely on the time for the orders to be executed. For example when designing a decentralized exchange, one can use a \emph{the call market} design instead of a time-sensitive order book~\cite{clark2014decentralizing} to side-step and disincentivize front-running by miners. In a call market design, the arrival time of orders does not matter as they are executed in batches.

The call market solution also pivots profitable gains that front-running miners stand to gain into fees that they collect~\cite{clark2014decentralizing}, removing the financial incentive to front-run. To the same end, Malinova~\cite{malinova2017market} proposes a design for a decentralized exchange which uses economic models in their trading market design to make front-running expensive and more costly than profitable. They split big investments into smaller ones using intermediaries --liquidity demander-- and liquidity providers to achieve this.

% one solution could be to remove multiple actors, meaning that on each "play" (order), the smart contract would be the market maker. it does not matter if there are multiple similar orders. similar to PoC of Velocity~\cite{eskandari2017feasibility}. Although there are other concerns about this specific design but not for front-running.

%TODO: inline talk about what these solutions are good for and if they fit Status ICO
